Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-21 theory.tex
starting case B description

>>>>

\begin{table}[htb]
\centering
  \caption{Summary of miss-use model properties.}
\begin{tabular}{l|ccc}
\toprule

Model                &    A                 & B                  & C  \\
\midrule
Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i*\beta_i, \theta_i$       \\
Optimised parameters & $\beta_i$            & $\theta_i$         & $\alpha_i, \beta_i$                     \\
Assays determination & blended              & ideal              & blended                  \\
Flow                 & unchanged            & scaled             & unchanged       \\

\bottomrule
\end{tabular}
  \label{tab:models}
\end{table}

\subsubsection{Case A}
The tuning method A does not re-optimize $\theta_i$ based on the true flow
enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed assay
($N'$), they do not change from stage to stage. According to equation
\eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, when the feed assay ($N$)
changes, then $\beta$ will change accordingly.  This breaks the ideal status of
the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.

In order to compute the proper product and tails assay at each stage, the
tails and the product from respectively the next and the previous stage must be
blended in order to determine the correct stage feed assay. As this is a obvious
cycling problem, an iterative solution has been chosen: all feed assays are
iteratively updated, blending the proper product and tails, then using the
updated feed assay, the new product and tail assays are recomputed. This process
is repeated until the change in assays is smaller than the set precision (1e-8
by default).
As the cut remain fixed at each stage the different flow do not need to be
recomputed.

\subsubsection{Case B}

The second method the cut value at each stage $\theta_i$, is retuned in order to
maintain the $\alpha_i$ and $\beta_i$ at their original values. As the cascade
remains ideal, the product and tail assay at each stages (and for the overall
cascade) is easily determined using equations \eqref{eqs:alphabeta}.

As the cuts values change, the flow rate between the different stage has to be
recomputed. Because the cascade is not reorganised (the number of cascade per
stage remain the same as the original design). The new flow rate are computed as the flow rate of cascade
